Intrusion Detection with \\ Genetic Algorithms and Fuzzy Logic

### 2013-11-21 Talk/Presentation.tex
Switched some sections around and removed some stuff.

\subsection{Determining the Accuracy of an Algorithm}
\begin{frame}
  \frametitle{Determining the Accuracy of an Algorithm}
%	\begin{itemize}
%		\item False positive (FP): intrusion detection system incorrectly identifies normal activity as being an attack. 
%		\item False negative (FN): intrusion detection system fails to identify harmful activity. 
%		\item True positive (TP): intrusion detection system correctly identifies activities to be attacks. 
%		\item True negative (TN): intrusion detection system correctly
%identifies activities to be normal.
%		\item Detection rate (DR): number of intrusions detected by the system divided
%by the total number of intrusions that happen.
%	\end{itemize}
\begin{table}
\begin{tabular}{cccc}
& & \multicolumn{2}{ c }{Predicted} \\
& & Not Attack & Attack \\ \cline{3-4}
\multicolumn{1}{ c }{\multirow{2}{*}{Actual} } &
\multicolumn{1}{ c| }{Not Attack} & True Negative (TN) & False Positive (FP)\\
\multicolumn{1}{ c }{} &
\multicolumn{1}{ c| }{Attack} & False Negative (FN) & True Positive (TP)\\
\end{tabular}
\end{table}
\linespace
	\begin{itemize}
		\item Detection rate (DR): number of intrusions detected by the system divided by the total number of intrusions that happen.
	\end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Using Fuzzy Genetic Algorithms]{Using Fuzzy Genetic Algorithms}

@@

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Using Genetic Algorithms]{Using Genetic Algorithms}
\subsection{Algorithm Overview}
\begin{frame}
  \frametitle{Algorithm Overview}
	\begin{itemize}
		\item The system is divided into 2 phases: a precalculation phase and a detection phase.
		\item In the precalculation phase, a set of chromosomes are created using training data. It takes network data as an input and outputs a set of chromosomes. Then this set of chromosomes is used in the detection phase.
		\item In the detection phase, selection, crossover, and mutation occur, and then the type of the data (whether it is an attack or normal behavior) is predicted.
	\end{itemize}
\end{frame}

\subsection{Experimental Design and Results}
\begin{frame}
  \frametitle{Experimental Design}
  \begin{columns}

@@

  \begin{column}{0.5\textwidth}
  \begin{table}
\caption{Number of records}
\begin{tabular}{lll}
  & Training & Testing \\
Normal & 97,280 & 60,593\\
Probe & 4,107 & 4,166\\
DoS         & 391,458 & 229,853\\
U2R & 52 & 228\\
R2L & 1,124 & 16,189\\
Total & 494,021 & 311,029\\
\end{tabular}
\end{table}
  \end{column}
  \end{columns}
\end{frame}

@@

%\multicolumn{1}{ c }{\% Correct} &
%\multicolumn{1}{ c| }{} & 76.9 & 54.7 & 92.0 & 6.4 & 50.0 \\
%\end{tabular}
%\end{small}
%\end{table}
	\begin{figure}
  \includegraphics[width=0.95\textwidth]{../resultsForGA.JPG}
  \caption{From [Hoque-Mukit-Bikas, 2012]}
  	\end{figure}

@@

\begin{itemize}
  \item The use of genetic algorithms and fuzzy logic in intrusion detection are effective ways of detecting attacks.
  \item The genetic algorithm had a high detection rate for denial of service attacks.
  \item The fuzzy genetic algorithm had a higher detection rate than a decision tree algorithm in most cases.
  \item Fuzzy genetic algorithms are good at detecting unknown attacks.
\end{itemize}

>>>>

\subsection{Determining the Accuracy of an Algorithm}
\begin{frame}
  \frametitle{Determining the Accuracy of an Algorithm}
\begin{table}
\begin{tabular}{cccc}
& & \multicolumn{2}{ c }{Predicted} \\
& & Not Attack & Attack \\ \cline{3-4}
\multicolumn{1}{ c }{\multirow{2}{*}{Actual} } &
\multicolumn{1}{ c| }{Not Attack} & True Negative (TN) & False Positive (FP)\\
\multicolumn{1}{ c }{} &
\multicolumn{1}{ c| }{Attack} & False Negative (FN) & True Positive (TP)\\
\end{tabular}
\end{table}
\linespace
	\begin{itemize}
		\item Detection rate (DR): 
	\end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Using Fuzzy Genetic Algorithms]{Using Fuzzy Genetic Algorithms}

@@

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Using Genetic Algorithms]{Using Genetic Algorithms}
\subsection{Experimental Design and Results}
\begin{frame}
  \frametitle{Experimental Design}
  \begin{columns}

@@

  \begin{column}{0.5\textwidth}
  \begin{table}
\caption{ }
\begin{tabular}{lll}
  & Training & Testing \\
Normal & 97,280 & 60,593\\
Probe & 4,107 & 4,166\\
DoS         & 391,458 & 229,853\\
U2R & 52 & 228\\
R2L & 1,124 & 16,189\\
Total & 494,021 & 311,029\\
\end{tabular}
\end{table}
  \end{column}
  \end{columns}
\end{frame}

@@

%\multicolumn{1}{ c }{\% Correct} &
%\multicolumn{1}{ c| }{} & 76.9 & 54.7 & 92.0 & 6.4 & 50.0 \\
%\end{tabular}
%\end{small}
%\end{table}

%	\begin{figure}
%  \includegraphics[width=0.95\textwidth]{../resultsForGA.JPG}
%  \caption{From [Hoque-Mukit-Bikas, 2012]}
%  	\end{figure}

@@

\begin{itemize}
  \item The use of genetic algorithms and fuzzy logic in intrusion detection are effective ways of detecting attacks.
%  \item The genetic algorithm had a high detection rate for denial of service attacks.
  \item The fuzzy genetic algorithm had a higher detection rate than a decision tree algorithm in most cases.
  \item Fuzzy genetic algorithms are good at detecting unknown attacks.
\end{itemize}
